Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-06-14 Paper/paper.tex
Easy Janzen Edits

We have used and outlined the merits of a number of existing testing tools and brought together the best among them to create what we feel is a fully-featured, easy to use, testing framework and workflow for web application development.

@@

We have found that this is not a solved problem by looking at some of the biggest web applications and websites around. A 2011 study showed that YouTube has at least eight errors, Apple has at least seven, Microsoft at least four, and the list goes on \cite{ErrorsInTheWild}. That may seem like a small amount for such large sites, but every error is an opportunity for malfunction and customer dissatisfaction.

\section{What Already Exists}
Web developers are not clueless, they understand that there is a need for testing of web applications. Unfortunately, web development is still a relatively new domain and developers have not come together to work on the problem of testing but rather have come up with their own proprietary solutions in isolation or merely on a per-project basis. Some of these tools have gained traction and become larger, more general, tools.

@@

There needs to be a framework in place for testing these multi-layer, multi-faceted web applications that is easy to use, allows for quick development, and is thorough in its coverage. This thesis will explore some of the most popular tools with the end goal of gathering the best tools out there and collecting them in one place. We will attempt to gather tools that work well together and cover all aspects of testing for an average developer, particular a developer who has experience in some field of software but may be new to web applications. Our hope is that this thesis will serve as a starting point and guide to future web application developers.

@@

In the very beginning, web applications were easy to write and test because the only code was plain HTML with a common set of HTML tags. It did not matter what browser was used to view the content because the viewer was always a home computer rendering plain HTML. As time progressed, individual browsers began offering additional features and web applications became more rich but harder to test because the developer would need to run their code on multiple browsers to make sure they all behaved similarly. In today's technological world, it is nearly impossible to run one's web application on all of the possible browser versions, configurations, and platforms that are available. Web applications are on home computers, phones, tablets, MP3 players, refrigerators \cite{SamsungFridge}, and a variety of other devices of varying sizes and capabilities. As a developer, one wants to target as many of those platforms as possible with a single code-base to save time and effort. A naive developer might just release an application on all platforms and hope for the best, but releasing on all platforms without testing will likely drive consumers away if the application fails on their given platform.

@@

\section{Web Features}
Here we'll discuss some of the prevalent technologies that recently appeared in web applications and development. By no means is this an exhaustive list, just a sampling of the more prominent ones.

\subsection{HTML5}
The latest revision of HTML is HTML5 which first debuted on Firefox back in 2009 \cite{EvolutionOfWeb}. HTML5 has not been officially recommended by the W3C (World Wide Web Consortium) who is the official keeper and recommender of web standards, however, there is a plan for final recommendation this year, 2014, called Plan 2014 \cite{Plan2014}. What this means is that in 2014 the W3C will release a stable HTML5 Recommendation which will make HTML5 an official standard and help universalize all the separate implementations.

@@

@@

\subsection{Client-side}
First, we'll address what a client is. The simple answer is: The User. The User's phone, computer, tablet, or other device communicating with a given website or application is the client. More specifically, the browser or service being using to communicate with the web is the client.

The client-side portion of an application interacts with the browser to request assets from the server and then displaying them in a human-readable way. The client-side also deals with the user interface and interactivity of a web page, e.g., the client-side displays a web form, the client fills in the information and clicks ``submit'' and the client-side packages up the data and sends it to the server.

@@

Clients communicate with the server through a request-response architecture. Clients send a request to the server, often with information attached, such as a form submittal or login, and the server returns a response with either a success/failure message, or additional data.

@@

In the above example there are two modules, \lstinline{Word} and \lstinline{Sentence}. Unit Testing the \lstinline{Word} is relatively simple because it is self-contained and only runs functions on the string given to it. Unit Testing the \lstinline{Sentence} module is tougher because of its reliance on \lstinline{Word}s. The goal of a good set of Unit Tests is to test as much of a module as possible in isolation from all other modules. This includes interactions between modules. In our example, testing the \lstinline{wordCount} function is a Unit Test because none of the \lstinline{Word} functionality is actually required. The other methods of \lstinline{Sentence} pose a problem because of their need to call \lstinline{Word} functions. Although there are ways to Unit Test those functions, that is beyond the scope of this overview and would only serve to confuse the reader.

@@

Integration Testing is important because it gives the developer a sense of what modules are actually producing correct results, as opposed to which modules are functioning as anticipated. This distinction is critical to make. Unit Tests ensure that individual modules function. Integration Tests are usually written in a way that is close to how they will actually be used in the final product, giving the developer a sense of which features are working and which are not.

@@

In an effort to automate this, some developers create ``User Stories'' which are automated tests that run a series of functions described by customers or an SRS. These User Stories are often written in a separate language that is more like English than code. The traditional User Story template is: ``As a \textless role\textgreater, I want \textless goal/desire\textgreater \space so that \textless benefit\textgreater.'' For example: ``As a supervisor, I want to find my employees by their employee ID.'' These user stories are then broken down into more specific steps that can be automated.

@@

@@

Web applications can be broken down into two general parts. There is functionality behind the scenes that drives the web page and there is the user interface of the web page that conveys the information to the user. Unit Testing frameworks are aimed at the functionality that drives the web page, not what the user sees.

@@

This relates to Jasmine is the way that the developer writes Jasmine tests. The idea behind Jasmine tests is that they read, as much as possible, like English sentences. As an example, the following is a valid Jasmine test:
\begin{lstlisting}
describe("Arithmetic Test", function () {
  it("should compute the addition of two numbers", function () {
    expect(1 + 2).toEqual(3);
  });

  it("should be able to subtract numbers", function () {
    var theAnswer = 10;
    expect(12 - 2).toEqual(theAnswer);
  });
});
\end{lstlisting}
The \lstinline{describe} statement creates a test suite to organize related tests. Each \lstinline{it} statement is generally one test with some number of \lstinline{expect} statements. The above code is quite readable even to someone with no coding experience.

@@

\subsubsection{Chai.js}
For the assertion library we chose Chai.js \cite{Chaijs}. It contains three different assertion APIs: an Expect API, a Should API, and a more general Assert API. The Expect API provides assertions of the form \lstinline{expect(myVar).to.equal(10);} or \lstinline{expect(myArr).to.have.length(10);}. The Should API has assertions of the form \lstinline{myVar.should.be.a('number');} or \lstinline{myArr.should.have.length(10);}. Finally, the Assert API has the more tried and true \lstinline{assert.equal(myVar, 10);} and \lstinline{assert.lengthOf(myArr, 10);}. The various APIs combined with Mocha's flexibility led to an experience that can appeal to a variety of different developers.

@@

QUnit provides another style of writing tests and grouping modules. QUnit's handling of asynchronous tests is nice because they are more explicitly stated for the casual read-through instead of an extra parameter or set of functions within the test itself.

\subsection{Intern}
Intern \cite{InternIO} is a hybrid Unit Testing and browser testing framework that aims to be an all-in-one testing framework. Intern has Unit Testing, browser testing, and code coverage information all built into the same tool. It is our intention to build a testing framework with all of these components, so finding a framework with all of them built-in was promising. Intern runs on its own server which give it access to the internals of the project, but caused problems when attempting to interact with a separate server running the Node.js application. We were unable to get the browser testing portion of Intern to work because of our inability to set up cross-server communication due to inexperience.

@@

  // Test code here
} ());
\end{lstlisting}

@@

%- TDD, BDD, Object methods
Intern uses Chai.js for assertion methods but has it built-in as opposed to Mocha in which the developer had to get it themselves. This gives the developer access to Expect, Assert, and Should testing methods. In addition to the various assertion styles, Intern offers three different testing interfaces: TDD, BDD, and Object. These testing interfaces effect how the general layout of test code looks. Here's a very quick example of the different layouts:
\begin{lstlisting}
// TDD
suite('TDD Suite', function () {
  test('test 1', function () {
    ...
  });
}

@@

The ability to mix assertion styles with testing interfaces provides a diverse way of writing tests. Some testing interfaces seems to fit better with certain assertion styles, but there's no restrictions on which can be used with which.

@@

%- Code Coverage!
Intern includes configurable code coverage metrics on tests by default. Running Unit Tests gives the number of lines covered (ran) by the tests. Code coverage is provided by another JavaScript library, Istanbul, created by Krishnan Anantheswaran \cite{Istanbul}.

@@

@@

Nightwatch is a Node.js module, and as such can easily installed and run via NPM and the commandline.

@@

\subsubsection{PhantomJS}
PhantomJS \cite{PhantomJS} came up repeatedly in our searches for testing frameworks as an option for headless browsing; it is the reason we had the idea to look into headless browsers. PhantomJS is a headless browser written using WebKit, which is what most of the web is based on. This means that running PhantomJS is nearly indistinguishable from a normal browser to any testing code.

@@

Mocha was chosen over QUnit because of the ability to structurally portray test suites. Although QUnit output a more thorough test summary, the ability to scan code more efficiently was of greater importance to us.

@@

\section{Our Implementation Configuration}
The following are the specs of the laptop that we used for the entirely of this research and implementation:
\begin{itemize}
  \item Model: 15-inch Macbook Pro, Late 2008
  \item OS: OS X 10.9.2, Mavericks
  % \item Processor: 2.53 GHz Intel Core 2 Duo
  % \item Memory: 4 GB 1067 MHz DDR3
  % \item Graphics: NVIDIA GeForce 9400M 256 MB
\end{itemize}
The point of listing the laptop specs is to show that our research and workflow was completed on an average, everyday laptop and does not require any kind of special hardware or software configurations. In addition, our setup instructions will be OS X based, but nearly all commands will work the same on another UNIX-based system.

@@

\subsection{Setting up Nightwatch}
Installing Nightwatch consists of just installing another NPM module. \lstinline{NPM install -g nightwatch}. In addition to Nightwatch, the developer needs Selenium. The easiest way is to just download the ``selenium-server-standalone'' JAR straight from the Google repository here: ``http://selenium-release.storage.googleapis.com/index.html''. Our tests ran using ``selenium-server-standalone-2.40.0'' but any version 2.40+ should work. Once the developer has the JAR and places it in a location they will remember, generally along with other similar executables in a bin or library directory, Nightwatch is ready to be configured and run. Nightwatch configuration happens in a JSON file that is pointed to when the developer executes Nightwatch.

@@

What we recommend is a Unit Test suite that runs on save. While this may seem excessive, it provides invaluable, instant feedback for regression assurance and new functionality. The way to set this up with the above tools is have a Grunt task that watches for changes in certain files and runs a script when the files change. Here's what our Grunt task looks like:
\begin{lstlisting}
module.exports = function(grunt)
{
  grunt.initconfig({
    watch: {
      test: {
          options: {
              spawn: false
          },
          files: ['**/*.js'],
          tasks: ['mochaTest']
      }
    },
    mochaTest: {
      test: {
          options: {
              reporter: 'spec',
              clearRequireCache: true
          },
          src: ['../../../../NetBeans/PolyXpressAuthor/test/unit/functional/*.js']
      }
    }
  });

@@

\section{PolyXpress (PX)}
Our major evaluation application was an in-house application called PolyXpress (PX)\cite{PX}. As the About page says, ``PolyXpress allows you to create location-based stories, build eTours, or create restaurant guides. It is the tool that will bring people to locations in order to entertain, educate, or provide amazing deals.''\cite{PX} Users can play or create ``Stories'', each of which consists of ``Chapters''. Each chapter consists of various ``Events''. Each ``Event'' generally give the user some sort of information, in the form of text, video, audio, or a picture. After the player has chosen a story, they must physically reach certain checkpoints to unlock chapters and events. Since the application requires physical movement, it works solely on devices with GPS, generally phones and tablets. Rather than put a series of pictures showing PolyXpress here, we will put them in the~\nameref{sec:appendix} at the end of the paper. To get a better sense of what PolyXpress does and looks like, we recommend looking at the~\nameref{sec:appendix} now.

@@

\subsection{``Contract-Driven Testing of JavaScript Code''}
Two individuals from the Albert Ludwigs University in Germany created a tool, JSConTest, that provides a framework for making contracts for a JavaScript program, allowing for guided random testing on inputs and outputs \cite{ContractDrivenTesting}. Contracts in JSConTest are comments above each function that are of the form ``type -> type''. More complicated forms can introduce parenthesis for function types. In general, JSConTest is useful for detecting type errors on input or output based on the operations performed within a function on the input and the result being output.

>>>>

We have used and outlined the merits of a number of existing testing tools and brought together the best among them to create what we believe is a fully-featured, easy to use, testing framework and workflow for web application development.

@@

We have found that this is not a solved problem by looking at some of the biggest web applications and websites around. A 2011 study showed that YouTube has at least eight errors, Apple.com has at least seven, Microsoft.com at least four, and the list goes on \cite{ErrorsInTheWild}. That may seem like a small amount for such large sites, but every error is an opportunity for malfunction and customer dissatisfaction.

\section{What Already Exists}
Web developers are not clueless, they understand that there is a need for testing of web applications. Unfortunately, web development is still a relatively new domain, and developers have not come together to work on the problem of testing but rather have come up with their own proprietary solutions in isolation or merely on a per-project basis. Some of these tools have gained traction and become larger, more general, tools.

@@

There needs to be a framework in place for testing these multi-layer, multi-faceted web applications that is easy to use, allows for quick development of both features and tests, and is thorough in its coverage. This thesis will explore some of the most popular tools with the end goal of gathering the best tools out there and collecting them in one place. We will attempt to gather tools that work well together and cover all aspects of testing for an average developer, particularly a developer who has experience in some field of software but may be new to web applications. Our hope is that this thesis will serve as a starting point and guide to future web application developers.

@@

In the very beginning, web applications were easy to write and test because the only code was plain HTML with a common set of HTML tags. It did not matter what browser was used to view the content because the viewer was always a home computer rendering plain HTML. As time progressed, individual browsers began offering additional features and web applications became more rich, but harder to test because the developer would need to run their code on multiple browsers to make sure they all behaved similarly. In today's technological world, it is nearly impossible to run one's web application on all of the possible browser versions, configurations, and platforms that are available. Web applications are on home computers, phones, tablets, MP3 players, refrigerators \cite{SamsungFridge}, and a variety of other devices of varying sizes and capabilities. As a developer, one wants to target as many of those platforms as possible with a single code-base to save time and effort. A naive developer might just release an application on all platforms and hope for the best, but releasing on all platforms without testing will likely drive consumers away if the application fails on their given platform.

@@

\section{Web Features}
Here we'll discuss some of the prevalent technologies that recently appeared in web applications and development. By no means is this an exhaustive list, just a sampling of the more prominent ones, particularly those that are integral to our evaluation application.

\subsection{HTML5}
The latest revision of HTML is HTML5 which first debuted on Firefox in 2009 \cite{EvolutionOfWeb}. HTML5 has not been officially recommended by the W3C (World Wide Web Consortium) who is the official keeper and recommender of web standards, however, there is a plan for final recommendation this year, 2014, called Plan 2014 \cite{Plan2014}. What this means is that in 2014 the W3C will release a stable HTML5 Recommendation which will make HTML5 an official standard and help universalize all the separate implementations.

@@

Node.js does have some drawbacks though. The biggest problem with Node.js is that it does not handle heavy computation well. Any CPU-intensive code will cause an application to hang where other server frameworks can offload tasks much more judiciously. This is due to Node.js' single threaded event loop. Another drawback is that Node.js is still immature in relation to other server frameworks such as Apache. It is not yet regarded as an enterprise framework.

@@

\subsection{Client-side}
First, we'll address what a client is. The simple answer is: The User. The User's phone, computer, tablet, or other device communicating with a given website or application is the client. More specifically, the browser or service being used to communicate with the web is the client.

The client-side portion of an application interacts with the browser to request assets from the server and then displays them in a human-readable way. The client-side also deals with the user interface and interactivity of a web page, e.g., the client-side displays a web form, the client fills in the information and clicks ``submit'' and the client-side packages up the data and sends it to the server.

@@

Clients communicate with the server through a request-response architecture. Clients send a request to the server, often with information attached, such as a form submittal or login, and the server returns a response with either a success message, a failure message, or additional data.

@@

In the above example there are two modules, \lstinline{Word} and \lstinline{Sentence}. Unit Testing the \lstinline{Word} is relatively simple because it is self-contained and only runs functions on the string given to it. Unit Testing the \lstinline{Sentence} module is tougher because of its reliance on \lstinline{Word}s. The goal of a good set of Unit Tests is to test as much of a module as possible in isolation from all other modules. This includes interactions between modules. In our example, testing the \lstinline{wordCount} function is a Unit Test because none of the \lstinline{Word} functionality is actually required. The other methods of \lstinline{Sentence} pose a problem because of their need to call \lstinline{Word} functions. There are ways to Unit Test these more complicated modules that have to do with creating ``mock objects.'' Mock objects are very simple objects whose behaviors and methods are entirely predictable. In our example, we would want to create a MockWord which would always return the same word or part of speech regardless of its arguments. In this way, we are not testing the MockWord functions in addition to the Sentence functions because we know exactly what to expect from the MockWord object.

@@

Integration Testing is important because it gives the developer a sense of what real features are working, as opposed to which individual modules are producing acceptable results. This distinction is critical to make. Unit Tests ensure that individual modules function. Integration Tests are usually written in a way that is close to how they will actually be used in the final product, giving the developer a sense of which real features are working and which are not as opposed to just knowing that a small part of the total result is right.

@@

Some developers and non-technical project members create ``User Stories'' which are short descriptions of desired functionality. The traditional User Story template is: ``As a \textless role\textgreater, I want \textless goal/desire\textgreater \space so that \textless benefit\textgreater.'' For example: ``As a supervisor, I want to find my employees by their employee ID.'' These user stories are then broken down by developers to specific steps that can be tested automatically.

@@

We are setting out to give developers a framework for running tests from the start of development. Our hope is that developers will take on a Test-Driven Development style in which they write tests first and then write the functionality so that bugs are detected soon after introduction. With the combination of Unit Testing and Continuous Integration, our workflow will give quick feedback so that the developer knows exactly what state their project is in at all times.

@@

Web applications can be broken down into two general parts. There is functionality behind the scenes that drives the web page and there is the user interface of the web page that conveys the information to the user. Unit Testing frameworks are aimed at the functionality that drives the web page, not what the user sees. This means that the Unit Testing frameworks were used to run both Unit Tests and Integration Tests for our ToDo application.

@@

This relates to Jasmine in the way that the developer writes Jasmine tests. The idea behind Jasmine tests is that they read, as much as possible, like English sentences. As an example, the following is a valid Jasmine test:
\begin{lstlisting}
describe("Arithmetic Test", function () {
  it("should compute the addition of two numbers", function () {
    expect(1 + 2).toEqual(3);
  });

  it("should be able to subtract numbers", function () {
    var theAnswer = 10;
    expect(12 - 2).toEqual(theAnswer);
  });
});
\end{lstlisting}
The \lstinline{describe} statement creates a test suite to organize related tests. Each \lstinline{it} statement is generally one test with some number of \lstinline{expect} statements. The above code is quite readable even to someone with no coding experience. Jasmine's Expect assertion come with 12 default assertions that can all be negated, meaning 24 assertions in all. The Expect API can be extended with custom assertions if needed.

@@

\subsubsection{Chai.js}
For the assertion library we chose Chai.js \cite{Chaijs}. It contains three different assertion APIs: an Expect API, a Should API, and a more general Assert API. The Expect API provides assertions of the form \lstinline{expect(myVar).to.equal(10);} or \lstinline{expect(myArr).to.have.length(10);}. The Should API has assertions of the form \lstinline{myVar.should.be.a('number');} or \lstinline{myArr.should.have.length(10);}. Finally, the Assert API has the more tried and true \lstinline{assert.equal(myVar, 10);} and \newline \lstinline{assert.lengthOf(myArr, 10);}. The various APIs combined with Mocha's flexibility led to an experience that can appeal to a variety of different developers.

Chai.js' Assert library has 50 different assertions to cover a wide range of tests. The Expect and Should APIs have around 33 standard assertions but because of the various ways to chain functions together, there are many more than just 33.

@@

QUnit provides another style of writing tests and grouping modules. QUnit's handling of asynchronous tests is nice because they are more explicitly stated for the casual read-through instead of an extra parameter or set of functions within the test itself. QUnit's built-in assertions only offer 10 different types, but their generic nature allows them to be flexible.

\subsection{Intern}
Intern \cite{InternIO} is a hybrid Unit Testing and browser testing framework that aims to be an all-in-one testing framework. Intern has Unit Testing, browser testing, and code coverage information all built into the same tool. It is our intention to build a testing framework with all of these components, so finding a framework with all of them built-in was promising. Intern runs on its own server which gives it access to the internals of the project, but caused problems when attempting to interact with a separate server running the Node.js application. We were unable to get the browser testing portion of Intern to work because of our inability to set up cross-server communication due to inexperience.

@@

  // Test code here
} ());
\end{lstlisting}
There are no assertions in the example because the focus is on how the modules are being loaded. Intern offers a variety of testing interfaces and so showing assertions without detailing that will lead to confusion.

@@

%- TDD, BDD, Object methods
Intern uses Chai.js for assertion methods but has it built-in as opposed to Mocha in which the developer had to get it themselves. This gives the developer access to Expect, Assert, and Should testing methods. In addition to the various assertion styles, Intern offers three different testing interfaces: TDD, BDD, and Object. These testing interfaces affect how the general layout of test code looks. Here's a very quick example of the different layouts:
\begin{lstlisting}
// TDD
suite('TDD Suite', function () {
  test('test 1', function () {
    ...
  });
}

@@

The ability to mix assertion styles with testing interfaces provides a diverse way of writing tests. Some testing interfaces seem to fit better with certain assertion styles, but there are no restrictions on which can be used with which.

@@

%- Code Coverage!
Intern includes configurable code coverage metrics on tests by default. Running Unit Tests gives the number of lines covered (run) by the tests. Code coverage is provided by another JavaScript library, Istanbul, created by Krishnan Anantheswaran \cite{Istanbul}.

@@

An example of one wrapper around Selenium is Nightwatch, which is outlined in the next section with example code included.

@@

Nightwatch is a Node.js module, and as such can be easily installed and run via NPM and the commandline.

@@

\subsubsection{PhantomJS}
PhantomJS \cite{PhantomJS} came up repeatedly in our searches for testing frameworks as an option for headless browsing; it is the reason we had the idea to look into headless browsers. PhantomJS is a headless browser written using WebKit, which is what most web browsers are based on. This means that running PhantomJS is nearly indistinguishable from a normal browser to any testing code.

@@

Mocha was chosen over QUnit because of the ability to structurally portray test suites. Although QUnit produced a more thorough test summary, the ability to scan code more efficiently was of greater importance to us.

@@

\section{Implementation Configuration}
The following are the specs of the laptop that we used for the entirely of this research and implementation:
\begin{itemize}
  \item Model: 15-inch Macbook Pro, Late 2008
  \item OS: OS X 10.9.2, Mavericks
  % \item Processor: 2.53 GHz Intel Core 2 Duo
  % \item Memory: 4 GB 1067 MHz DDR3
  % \item Graphics: NVIDIA GeForce 9400M 256 MB
\end{itemize}
The point of listing the laptop specs is to show that our research and workflow was completed on an average, everyday laptop and does not require any kind of special hardware or software configurations. In addition, our setup instructions will be OS X based, but nearly all commands will work the same on another UNIX-based system.

@@

\subsection{Setting up Nightwatch}
Installing Nightwatch consists of just installing another NPM module. \lstinline{NPM install -g nightwatch}. In addition to Nightwatch, the developer needs Selenium. The easiest way is to just download the ``selenium-server-standalone'' JAR straight from the Google repository here: \newline http://selenium-release.storage.googleapis.com/index.html. Our tests ran using ``selenium-server-standalone-2.40.0'' but any version 2.40+ should work. Once the developer has the JAR and places it in a location they will remember, generally along with other similar executables in a bin or library directory, Nightwatch is ready to be configured and run. Nightwatch configuration happens in a JSON file that is pointed to when the developer executes Nightwatch.

@@

What we recommend is a Unit Test suite that runs on save. While this may seem excessive, it provides invaluable, instant feedback for regression assurance and new functionality. The way to set this up with the above tools is have a Grunt task that watches for changes in certain files and runs a script when the files change. Here's what our Grunt task looks like:
\begin{lstlisting}
module.exports = function(grunt)
{
  grunt.initconfig({
    watch: {
      test: {
          options: {
              spawn: false
          },
          files: ['**/*.js'],
          tasks: ['mochaTest']
      }
    },
    mochaTest: {
      test: {
          options: {
              reporter: 'spec',
              clearRequireCache: true
          },
          src: ['PolyXpressAuthor/test/unit/functional/*.js']
      }
    }
  });

@@

\section{PolyXpress (PX)}
Our major evaluation application was an in-house application called PolyXpress (PX)\cite{PX}. As the About page says, ``PolyXpress allows you to create location-based stories, build eTours, or create restaurant guides. It is the tool that will bring people to locations in order to entertain, educate, or provide amazing deals.''\cite{PX} Users can play or create ``Stories'', each of which consists of ``Chapters''. Each chapter consists of various ``Events''. Each ``Event'' generally gives the user some sort of information, in the form of text, video, audio, or a picture. After the player has chosen a story, they must physically reach certain checkpoints to unlock chapters and events. Since the application requires physical movement, it works solely on devices with GPS, generally phones and tablets. Rather than put a series of pictures showing PolyXpress here, we will put them in the~\nameref{sec:appendix} at the end of the paper. To get a better sense of what PolyXpress does and looks like, we recommend looking at the~\nameref{sec:appendix} now.

@@

\subsection{``Contract-Driven Testing of JavaScript Code''}
Two individuals from the Albert Ludwigs University in Germany created a tool, JSConTest, that provides a framework for making contracts for a JavaScript program, allowing for guided random testing on inputs and outputs \cite{ContractDrivenTesting}. Contracts in JSConTest are comments above each function that are of the form ``type -\textgreater \space type''. More complicated forms can introduce parenthesis for function types. In general, JSConTest is useful for detecting type errors on input or output based on the operations performed within a function on the input and the result being output.
